%% ----------------------------------------------------------------
%% Goal.tex
%% ----------------------------------------------------------------
\chapter{Project Goals} \label{Chapter:Goals}

\section{The problem}

With the rapid growth of integrated circuit manufacture technology, processing power was just enough to realise computation intensive computer vision algorithms by a small form factor mobile device. Such a battery powered mobile device provides considerable flexibility and is an essential part in robotic systems, artificial intelligence and machine learning. However, mobile devices generally have limited processing power, memory, storage and energy, but video processing algorithms involves lots of computations, hence could be the most power intensive and time consuming part in such application.

\section{Aims}

The aim of this project was to investigate ways to reduce overall power consumption of camera based real-time object detection and tracking applications, by applying feedback control of the camera module based on previous tracking results and utilising existing camera hardware capabilities including downsampling and cropping instead of software algorithms, while keeping a sensible accuracy. By doing so the average computation time would be dramatically reduced, hence reducing the overall power consumption.

The targets to be achieved are:

\begin{itemize}
  \item Development of a basic object tracking system, identify algorithms suitable for real-time operation, minimise operating system overheads.
  \item Interfacing camera module with the embedded system, expose control functions.
  \item Develop and analyse automatic camera frame rate reduction.
  \item Develop and analyse hardware downsampling and cropping.
  \item If time allows, object recognition may be implemented.
\end{itemize}
