\chapter{Project management}

\section{Risk assessment}

\section{Time management}

The topic of project changed once during week 7 in semester 1. The previous topic (\aref{Appendix:brief_prev}) was about reducing power consumption for algorithms that are utilising General Purpose GPU (GPGPU) technique, by adaptively controlling calculation precision. The NVIDIA Jetson TK1 development platform was decided to be used in this project. However, after investigated into the topic and experimented with some algorithms, the purposed precision control did not contribute significant impact on computation quality. Not much power saving would be possible to be made.

Therefore, I decided to change the project topic. The current project topic (\aref{Appendix:brief}) was quickly determined. The same hardware platform was still used, so that the time invested in the previous project was not wasted. Therefore, I was able to quickly catch up with the progress.

The Gantt chart was also changed due to project topic changing, as shown in \aref{Appendix:gantt}. The time invested for previous project topic was treated as background reading.
\todo{GANTT CHART UPDATE}

\section{Backing up}

%Source code management.
%Documents and materials.

The git version control system \cite{git} was used in this project. It has the feature that allows multiple users collaborate on the same repository. However, this is an individual project, git was used purely for backing up source code version history and synchronisation between multiple devices. Well-known git hosting website GitHub \cite{github} and university's SourceKettle server \cite{sourcekettle} were used for multiple backups.

All documents, background literals and materials used by the project were backed up using Microsoft's OneDrive service.

%\section{Remaining work}

%\begin{itemize}
%  \item Movement tracking based on blob detection (Section \ref{bg:tracking}, \ref{impl:tracking}).
%  \item A camera module need to be ordered and interfaced.
%  \item Automatic frame rate reduction based on tracking result.
%  \item Hardware downsampling and cropping based on ROI.
%  \item If time allows, energy-efficient object recognition may be implemented.
%\end{itemize}
